%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.4, 27 July 2018) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% IF YOU ARE USING ACADEMICONS ICONS (Mainly for \orcid BUT ALSO FOR OTHERS LIKE \aiOutlineGoogleScholar):
%% Add "academicons" option to \documentclass, and compile with XeLaTeX or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

\documentclass[10pt,a4paper]{altacv} % REMOVED ragged2e from class options

%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% 
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font 
%% folder.


% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm} % Adapted from example

% Change the font if you want to.

% If using pdflatex:
% \usepackage[T1]{fontenc} % REMOVED - altacv handles this for pdflatex
% \usepackage[utf8]{inputenc} % REMOVED - altacv handles this for pdflatex
\usepackage[default]{lato} % KEPT - This is your specific font choice for pdflatex

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Navy}{HTML}{000080}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Navy}
\colorlet{accent}{Navy}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey} % Consider \colorlet{body}{SlateGrey} for better readability
                           

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle} 

\usepackage[colorlinks,urlcolor=accent]{hyperref} 

\usepackage{paracol} % For two-column layout
\usepackage[document]{ragged2e} % ADDED - To apply ragged right justification, similar to the example
\usepackage{textcase} % For \MakeTextUppercase


\begin{document}

\name{Felipe Mediavilla Levinson}
\tagline{\small 
Data Analyst \& Engineer specializing in automation, machine learning, and full-stack development. Experienced in building scalable tools to enhance forecasting, streamline operations, and reduce manual work.}
\personalinfo{%
  \location{Santiago, Chile} 
  \email{frmediavilla@uc.cl}
  \phone{+56 976309980}
  \homepage{https://felipemedlev.com} 
  \github{github.com/felipemedlev}
}

\makecvheader 

\AtBeginEnvironment{itemize}{\small}
\columnratio{0.62}

\begin{paracol}{2}

\cvsection{Experience}

\cvevent{Senior Data Analyst | Automation Engineer}{Falabella S.A.}{Aug 2022 -- Present}{Santiago, Chile}
\begin{itemize}
\item Reduced \textbf{150+ analyst-hours weekly} by automating manual tasks using Python and SQL.
\item Built \textbf{ML models for financial forecasting} and cost pass-through analysis.
\item Created full-stack \textbf{Rebate App} (Next.js + Django), cutting approval time by 40\%.
\item Developed \textbf{anomaly detection} scripts for early flagging of cost center deviations, reducing financial reporting errors.
\item Automated SAP client creation by converting SharePoint data into XML inputs readable by SAP.
\item Built \textbf{KPI dashboards} in Tableau and Looker Studio, consumed by 50+ stakeholders.
\item Parsed and structured XBRL financial data to enhance regulatory reporting automation.
\item Deployed internal tools on \textbf{GCP}, ensuring fast, secure access across distributed teams.
\item Built a \textbf{PDF-to-Excel validator} to check financial reports before CMF submission, reducing regulatory risk from upload errors.
\item Consolidated sales data from \textbf{25+ transactional tables} into a unified source of truth used organization-wide.
\end{itemize}
\divider

\cvevent{Financial Planning Analyst}{Softys S.A.}{Aug 2021 -- Aug 2022}{Santiago, Chile}
\begin{itemize}
\item Supported annual budget consolidation and strategic alignment.
\item Led monthly closings and variance analysis for executive reporting.
\end{itemize}
\divider

\cvevent{Industrial Consultant}{TICGAS}{Jul 2021}{Santiago, Chile}
\begin{itemize}
\item Built an in-house product costing system and developed a linear optimization model, boosting revenue by 20\% without increasing operational inputs.
\end{itemize}
\divider

\cvevent{Underwater Robotics Interface Developer (Intern)}{CoMPAS Lab}{Apr 2021 -- Sep 2021}{Santiago, Chile}
\begin{itemize}
\item Designed navigation algorithms and GUI for autonomous robots.
\end{itemize}
\divider

\cvevent{Project Management Intern}{SQM}{Dec 2019 -- Mar 2020}{Antofagasta, Chile}
\begin{itemize}
\item Created standardized project management protocols to track and reduce cost overruns.
\item Proposed evaporation control system, later implemented in operations.
\end{itemize}

\switchcolumn

\cvsection{Education}

\cvevent{Civil Industrial Engineer (with Distinction)}{PUC Chile}{2015 -- 2021}{Santiago, Chile}
\begin{itemize}
\item Diploma in Mechanical Engineering; thesis in CFD fire simulations (Python).
\item TA for “Control of Mechanical Systems” (2 semesters).
\item Led design teams for \textbf{VSolar} (EV challenge) and \textbf{RobotX} (autonomous boats).
\end{itemize}

\cvsection{Side Projects}

\cvevent{Sille | \normalfont{\textit{Full-Stack Developer (Solo Startup)}}}{}{2024}{}
\begin{itemize}
\item Built e-commerce platform (React/Expo + Django) for niche perfumery.
\item Integrated \textbf{ML recommender system} for personalized product suggestions.
\item Architected API, data models, and frontend onboarding flow.
\item \faGlobe\hspace{0.5em} \href{https://sille.cl}{http://sille.cl}
\end{itemize}
\divider

\cvevent{Ariesanalytics.ai | \normalfont{\textit{Frontend Developer}}}{}{2024}{} 
\begin{itemize}
\item Created company site using \textbf{Next.js} with responsive UX.
\item \faGithub\hspace{0.5em} \href{https://github.com/felipemedlev/ariesdata}{GitHub: ariesdata}
\end{itemize}

\cvsection{Technical Skills}

\cvtag{Python} \cvtag{SQL} \cvtag{Git} \cvtag{Bash} \cvtag{Excel} \cvtag{PowerApps}
 \cvtag{Django} \cvtag{React} \cvtag{Next.js} \cvtag{Pandas} \cvtag{Scikit-learn} \cvtag{NumPy}
\cvtag{GCP} \cvtag{PostgreSQL} \cvtag{Tableau} \cvtag{Looker}

\cvsection{Languages}
\cvskill{Spanish (Native)}{5}
\cvskill{English (C1)}{4}
\cvskill{Hebrew (Basic)}{2}
\cvskill{Portuguese (Basic)}{1}

\end{paracol}

\end{document}
